### 2017-08-17 Documents/bootcamp_syllabus.tex
update links to website
Updating Syllabus

\documentclass[11pt]{article}

\input{../LaTeX/preamble.tex}

% document starts here
\begin{document}
\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
\input{../LaTeX/header.tex}

\bigskip\bigskip
\centerline{\Large \bf Data Bootcamp:  Syllabus}
\centerline{Revised: \today}

\section*{Overview}

Data Bootcamp is about nuts and bolts data analysis. You will learn about economic, financial, and business
data, and enough about computer programming to work with it effectively.
Applications include some or all of: leading economic indicators; emerging market country indicators;
bond and equity returns; stock options; education and income; income by zip code; long tail sales data; innovation diffusion curves; and many others.
We will use Python, a popular high-level computer language that's widely used in finance, consulting,
technology, and other parts of the business world.
``High-level'' means it's less painful than most (the hard work is done by the language),
but it's a serious language with extensive capabilities.
``Data analysis'' means primarily graphical descriptions that summarize data
in ways that are helpful and informative.
``Bootcamp'' is a reminder that expertise takes work. Don't worry, it's worth it.
{\bf You will be more valuable to current and future employers.\/}
And you will be able to do more things more efficiently than
friends who rely on Excel.

If you're not convinced --- or even if you are ---
we have a more elaborate sales pitch on the
\href{http://databootcamp.nyuecon.com/}{course website}.

@@

\section*{Requirements}

@@

Eveything you need, including this document, is posted on
the {\bf course website\/}:
%
\vspace{-0.15in}
\begin{center}
\url{http://databootcamp.nyuecon.com/}
\end{center}
\vspace{-0.15in}
%
The {\bf book\/} has its own site,
\vspace{-0.15in}
\begin{center}
\url{https://www.gitbook.com/book/nyudatabootcamp/data-bootcamp/details}
\end{center}
\vspace{-0.15in}
%
There's a link to it on the course site.
We will not use NYU Classes.

>>>>

%\documentclass[11pt]{article}

%%%%%%%%%%%%%%%%%%%%%% Stock Preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{../LaTeX/undergrad_preamble.tex}

%%%%%%%%%%%%%%%%%%%%%%Headers and Footers%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{headandfoot}
\runningheadrule
\firstpageheadrule
\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp}
\runningheader{Data Bootcamp}{}{Syllabus: ECON-UB.0011.02}
\runningfooter{}{}{}

\begin{document}
\centerline{\Large\bf Syllabus:  Data Bootcamp}
\vspace{3mm}
\centerline{\large\bf ECON-UB.0232 $|$ Fall 2017}
\vspace{3mm}
\centerline{\bf Revised:  \today}

\bigskip
%\vspace{-.25cm}

Data Bootcamp is about nuts and bolts data analysis. You will learn about economic, financial, and business
data, and enough about computer programming to work with it effectively. Applications include some or all of: leading economic indicators; emerging market country indicators; bond and equity returns; stock options; education and income; income by zip code; long tail sales data; innovation diffusion curves; and many others.

We will use Python, a popular high-level computer language that's widely used in finance, consulting,
technology, and other parts of the business world. ``High-level'' means it's less painful than most (the hard work is done by the language), but it's a serious language with extensive capabilities.

``Data analysis'' means primarily graphical descriptions that summarize data
in ways that are helpful and informative. ``Bootcamp'' is a reminder that expertise takes work. Don't worry, it's worth it. {\bf You will be more valuable to current and future employers.\/} And you will be able to do more things more efficiently than friends who rely on Excel.

If you're not convinced|or even if you are|we have a more elaborate sales pitch on the
\href{https://nyu.data-bootcamp.com/}{course website}.

@@

\subsubsection*{About the Instructor}
\href{http://www.waugheconomics.com}{Professor Michael Waugh} \\
Email: mwaugh@stern.nyu.edu\\
Office: KMC 7-74\\
Phone: 212-998-0288\\
Office hours: TBA, Monday and Wednesday.

\subsubsection*{Where and When}
Monday and Wednesday \\
%Section \#2: TISCH UC24, 3:30PM - 4:45PM

\subsection*{Requirements}

@@

Eveything you need, including this document, is posted on
the {\bf course website\/}:
%
\vspace{-0.15in}
\begin{center}
\url{http://nyudatabootcamp.github.io/website/}
\end{center}
\vspace{-0.15in}
%
The {\bf book\/} has its own site,
\vspace{-0.15in}
\begin{center}
\url{https://www.gitbook.com/book/nyudatabootcamp/data-bootcamp/details}
\end{center}
\vspace{-0.15in}
%
There's a link to it on the course site.
We will not use NYU Classes.
